---
title: "CGIAR Scientometrics"
author: "Melanie BACOU"
output: 
  html_notebook: 
    toc: yes
    toc_depth: 2
---

Testing Neo4j graph database with R using a collection of CGIAR publications, institutions, and authors.


```{r setup}

library(data.table)
library(RNeo4j)

graph <- startGraph("http://localhost:7474/db/data/")
# If you have authentication enabled, pass your username and password.
# graph <- startGraph("http://localhost:7474/db/data/", username="neo4j", password="password")

browse(graph, viewer=FALSE)


```

With Neo4j 2.2, a new, massively parallel and scalable CSV importer was released as part of the product. We want to use it to import publication data into Neo4j. The tool is located in `path/to/neo4j/bin/neo4j-import` and is used as follows.

There's also an open-source ETL tool **Structr** at https://structr.org/.


```{bash, eval=FALSE}

# Structr
wget https://structr.org/repositories/snapshots/org/structr/structr-ui/2.1.0-SNAPSHOT/structr-ui-2.1.0-20161112.121104-20.deb
sudo dpkg -i structr-ui-<version>.deb.

# Structr will be installed in /usr/lib/structr-ui, log file is /var/log/structr-ui.log
sudo service structr-ui start.
# Go to http://localhost:8082/structr#pages.
# Login with the default credentials admin/admin.

bin/neo4j-import --into cgiar.db --id-type string \
                 --nodes:Publication sciencedirect_pubs.csv \
                 --nodes products.csv  \
                 --nodes orders_header.csv,orders1.csv,orders2.csv \
                 --relationships:CONTAINS order_details.csv \
                 --relationships:ORDERED customer_orders_header.csv,orders1.csv,orders2.csv

```


```{r data}

pubs <- fread("./data/sd/sciencedirect_pubs.csv")
auth <- fread("./data/sd/sciencedirect_authors.csv")
pubs_x <- fread("./data/sd/sciencedirect_pubs_meta.csv")
auth_x <- fread("./data/sd/sciencedirect_pubs_meta.csv")

```


